---
title: "Johan Ibrahim's CV"
author: Johan Ibrahim
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'custom.css', 'resume']
    self_contained: true
---
<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">

<!-- final academic icons -->
 
<!-- start font awesome -->
<script src="https://kit.fontawesome.com/e82584e357.js" crossorigin="anonymous"></script>

 
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1_Y3HPpenl9Q0rovGZUmto6kxSCrtv8BsTGSfdk-xdXk/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
=================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at drjohan.github.io/drjohancv/index.html")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/DrJohan/drjohancv/raw/main/drjohan_cv.pdf).")
}
```

Contact {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> johan@ms.rcsiucd.edu.my
- <i class="fa fa-twitter"></i> [Twitter: `@`DrJohan81](https://twitter.com/BeaMilz)
- <i class="fa fa-github"></i> [GitHub: `@`DrJohan](https://github.com/drjohan)
- <i class="fab fa-orcid"></i> <a href='https://orcid.org/0000-0002-1437-5183'> Orcid Johan </a>  
- <i class="fa fa-home"></i> [Johan Ibrahim](https://drjohan.rbind.io)
- <i class="fab fa-linkedin-in"></i>  [Johan_Ibrahim](http://linkedin.com/in/johan_ibrahim)

Research Skills {#skills}
---------------------------------------------------------------------------------

- Infectious Disease Modelling
- Scientific Literature Review
- Regression Analysis
- Time to Event Analysis
- Experimental Design and Analysis
- Artificial Intelligence

Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```


Main
================================================================================

Johan Ibrahim {#title}
--------------------------------------------------------------------------------

Hi!! My name is Johan Ibrahim. Currently I'm working as Clinical Research Associate with [Aesculape CRO Belgium-Singapore](https://www.aesculape.com). 


I describe myself as dedicated, highly motivated and enthusiastic medical graduate with in-depth knowledge of research design and methodologies, medical statistic, big data capture, curation, manipulation and visualization and has been certified Good Clinical Practice researcher from National Institute of Health (NIH) Malaysia.Able to use own initiative and work as part of a team under pressure to meet challenging deadlines/objectives. 


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Selected Short Courses Attended {data-icon=book} 
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('short_courses')
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------
::: aside

I'm a medical doctor by training. In the past, I've been served people in Indonesia and Malaysia and actively involve in search and rescue during Earthquake in Indonesia, 2006. Then, I decided to have a change in career after being inspired by my mentor Prof Ronan Conroy and decided to pursue a career in research as medical statistician cum data scientist. Since joining Aesculape CRO, I've been involved in multiple clinical trial including RWE/RWD research. I'm alsohighly motivated and results-oriented Clinical Research Associate II with 5 years of experience in cardiology, neurology, and dermatology. Proven ability to manage all aspects of clinical trials, from protocol development to close-out, while ensuring regulatory compliance and meeting aggressive deadlines. Strong track record of fostering collaboration with investigators and stakeholders to deliver successful clinical research programs. 

:::

```{r}
CV %<>% print_section('working_experience')
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------
::: aside

Played a key role in managing multiple clinical trials across cardiology, neurology, and dermatology, ensuring all phases from start-up to close-out adhered to scientific protocols, regulatory requirements, and ethical guidelines.

Successfully achieved on-time completion of study milestones by developing and implementing effective site management plans, including investigator recruitment, site initiation visits, and ongoing monitoring visits.

Proactively identified and mitigated potential regulatory risks by maintaining a deep understanding of ICH-GCP guidelines and communicating effectively with investigators and sponsors to ensure all studies remained compliant.


:::





```{r}
CV %<>% print_section('research_projects')
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

Selected Events Attended {data-icon=calendar-check}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('events_attended')
```


<!-- Selected Data Science Writing {data-icon=chart-line} -->
<!-- -------------------------------------------------------------------------------- -->

::: aside

The source code is available <i class="fa fa-github"></i> [Github](https://github.com/DrJohan/drjohancv).
Last updated on `r Sys.Date()`. The most recent version of this CV is [available here](drjohan.github.io/drjohancv/index.html)



:::








